---
  title: "meta"
author: "Mariia Vlasova, Yuheng Sun, Janet Chik"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
  wrap: 72
---

```{r setup}
knitr::opts_chunk$set(echo = FALSE,
                      results = 'hide',
                      warning = FALSE,
                      message = FALSE,
                      include = FALSE)
```

# Intro

```{r}
#install_github("elizagrames/litsearchr", ref="main",force = TRUE)

pacman::p_load(devtools,remotes, BiocManager, ggplot2, ggpubr, patchwork, GGally, magrittr, dplyr, tidyverse, openxlsx, tidylog, broom, broom.mixed, metafor, MuMIn, parallel, orchaRd, rotl, ape, ggtree, svglite, easystats, report, performance, tinytable, modelsummary, emmeans, ggsignif)
options(scipen = 999)
options(digits = 10)
```

# Litsearchr

## Get keywords from litsearchr

```{r}
# Import naive search results (from (ALL=("parental age" AND "offspring" AND "telomere length" ) AND DT=(Article)))
naive <- litsearchr::import_results(file="savedrecs.ris")

# Extract keywords from Keywords, Titles, Abstracts
keywords <- litsearchr::extract_terms(keywords = naive[, "keywords"],
                                      method = "tagged",
                                      min_n = 1)
titles <- litsearchr::extract_terms(text = naive[, "title"],
                                    method = "fakerake",
                                    min_freq = 3, min_n = 1)
abstracts <- litsearchr::extract_terms(text=naive[, "abstract"],
                                       method="fakerake",
                                       min_freq=3, min_n=1)
# combine all
naive <- unique(c(keywords,titles,abstracts))
capture.output(naive, file = "naive.txt")
```

Selected and grouped search terms manually from the file

```{r}
# Check if the full-term search contains all selected as GS articls (titles cleaned to keep only letters)
full_search <- litsearchr::import_results(file="871savedrecs.ris") %>% 
  mutate(title_clean = tolower(trimws(gsub("<.*?>", "", title)))) %>% 
  mutate(title_clean = gsub("[^a-z0-9\\s-]", "", title_clean))

GSarticles <- litsearchr::import_results(file="articles.ris") %>% 
  mutate(title_clean = tolower(trimws(gsub("<.*?>", "", title)))) %>% 
  mutate(title_clean = gsub("[^a-z0-9\\s-]", "", title_clean)) %>% 
  mutate(in_new_results = title_clean %in% full_search$title_clean)

# none are missing
GSarticles %>% filter(!in_new_results) %>% select(title)
```

# Meta-analysis

## Import and convert data

```{r}

d <- read.csv("MV_meta.csv", header = TRUE, skip = 1) %>%
  mutate(year = as.numeric(format(as.Date(PubDate, format = "%Y-%m-%d"), "%Y")), year.c = scale(year, scale = FALSE),
         across(c(year,ParSex, OffSex, Species, SpermProdSeason, Tissue, MethFact, OffAgeTL, W_B_PEff, EnvEff, EnvCond, MF_ID), as.factor),
         Tissue = fct_other(Tissue, keep = c("Leucocytes", "Erythrocytes"))) # put all tissues that are not Leukocytes or Erythrocytes to "Other" #, Method = ifelse(MethFact %in% c("TFR", "qPCR"), MethFact, "Other")
d <- droplevels(d[!d$EnvCond == "Captive",]) # drop Salmon study since it's only one "captive"

# Transform data to escalc to use with models from metafor
dd <- escalc(measure = "ZCOR", # Fisher's r-to-z transformed correlation coefficient
             ri = CorCoefCorrected, # ri, vector with the raw correlation coefficients
             ni = n_obs, # ni, the corresponding sample sizes, here n_obs
             var.names=c("Zr","ZrVar"),
             data = d)

# This results in a dataframe with two added columns: Zr, which is the vector with the observed effect sizes (so r-to-z) and ZrVar, which is the vector with the corresponding sampling variances

dd <- dd %>% mutate(ZrSE = sqrt(ZrVar)) # Zr standard error = square root of the sampling variance

meanzr <- mean(dd$Zr)
sdzr <- sd(dd$Zr)
minzr <- min(dd$Zr)
maxzr <- max(dd$Zr)
```

```{r}
# "Construct variance-covariance matrix of dependent sampling errors of effect sizes (i.e., the V matrix in rma.mv)"
V = vcalc(vi = ZrVar, cluster = StudyID, data=dd)
```

```{r}
report(dd$Zr)
```

```{r}
#sessionInfo()
#report(sessionInfo())
# report_packages(include_R = FALSE)
# cite_packages(prefix = "> ")
#report_system()
```


## M0. Global intercept model

```{r echo=T}
m0 <- rma(Zr,ZrVar,
          data = dd, method = "ML", slab=paste(Author.s., sep=", "))
summary(m0)
```

What is Zr adjusted for study, estimate, phylogeny?
```{r}
rma.mv(Zr, ZrVar, random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny),
                 R = list(Phylogeny = PhyloMatrix),
                 data = dd, method = "ML") # -0.0682
```

### Histogram of Fisher z transformed correlation coefficient

```{r, echo=T}
#Fisher's z transformed correlation coefficient histogram
histZr <- ggplot(data = dd, aes(x = Zr))+
  geom_histogram(binwidth = 0.05, colour = "black", fill = "grey90") +
  geom_vline(xintercept = meanzr, linetype = "dashed", linewidth = 0.75, colour = "purple") +
  geom_vline(xintercept = -0.0682, linetype = "dashed", linewidth = 0.75, colour = "seagreen",show.legend=F) + #xintercept = -0.0682 is Zr adjusted for study, estimateID, phylogeny
  xlab("Fisher's z transformed correlation coefficient") +
  ylab("Frequency") +
  scale_x_continuous(breaks = seq(-1, 1, 0.1)) +
  scale_y_continuous(breaks = seq(0,40,5), limits = c(0,37), expand = c(0,0)) +
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
        
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        
        axis.ticks = element_line(colour = "black"),
        axis.line = element_line(colour = "black"),
        
        axis.text.x = element_text(size = 10,family = "Arial", colour = "black", margin=margin(t=5)),
        axis.text.y = element_text(size = 10, family = "Arial", colour = "black"),
        axis.title.x = element_text(size = 12, family = "Arial", colour = "black",margin=margin(t=10)),
        axis.title.y = element_text(size = 12, family = "Arial", colour = "black",margin=margin(r=10)))
histZr
ggsave(histZr, filename = "histZr.svg", bg = "white", width=(20*(6/7)), height=(20*(3/7)), units = c("cm"))
```


### Forest plot of the individual estimates

```{r}
svglite::svglite(filename="forestplot.svg", width = 10, height = 30,
                 pointsize = 14, bg = "white")

par(tck=-0.01, mgp=c(2.5,0.5,0), mar=c(5,0,0,0))
forest(m0, order="obs", shade="zebra",
       alim = c(-3,4), at=seq(-1,1, by=0.25),
       efac=c(0,1,1), col="black", psize=0.75, cex=0.65, # added diamond
       cex.lab=1, #x-axis title
       cex.axis=1, #x-axis labels
       lty=c("solid","blank"), # remove horizontal line at top of plot
       xlim=c(-2,1.5), # adjust horizontal plot region limits
       header="Author(s) and Year")
dev.off()
```

### Forest plot with aggregated values

```{r}
agg <- aggregate(dd, cluster=StudyID, V=vcov(m0, type="obs"), addk=TRUE)
m_agg <- rma(Zr, ZrVar, data = agg, method = "ML", slab=paste(Author.s., sep=", "))

svglite::svglite(filename="forestplotagg.svg", width = 12, height = 16, pointsize = 16, bg = "transparent")

forest(m_agg, xlim=c(-3,2), mlab="Pooled Estimate", header="Author(s) and Year",
       shade="zebra", lty=c("solid","blank"),
       alim = c(-3,4), at=seq(-1,1, by=0.25), order="obs",
       efac=c(0,1,1), col="black", psize=0.75,
       fonts = "Arial",
       cex=1,
       cex.lab=1, #x-axis title
       cex.axis=1, #x-axis labels
       ilab=ki,ilab.xpos=-1.5)
text(-1.5, m_agg$k+2.1, c("Estimates"), cex=1, font=2)
dev.off()
```

### Forest plot with phylogenetic tree

```{r}
MSp <- rma.mv(Zr,ZrVar,
              mods = ~ Phylogeny -1,
              random = list(~ 1|StudyID, ~1|EstimateID),
              data = dd, method = "REML")
MSp

dd = dd %>% mutate(CommonName = case_when(
    Species == "Meles meles" ~ "European badger",
    Species == "Acrocephalus sechellensis" ~ "Seychelles warbler",
    Species == "Homo sapiens" ~ "Human",
    Species == "Ovis aries" ~ "Domestic sheep",
    Species == "Lacerta agilis" ~ "Sand lizard",
    Species == "Sterna hirundo" ~ "Common tern",
    Species == "Gulosus aristotelis" ~ "European shag",
    Species == "Tachymarptis melba" ~ "Alpine swift",
    Species == "Acrocephalus arundinaceus" ~ "Great reed warbler",
    Species == "Plocepasser mahali" ~ "White-browed sparrow-weaver",
    Species == "Corvus monedula" ~ "Western jackdaw",
    Species == "Passer domesticus" ~ "House sparrow",
    Species == "Pagodroma nivea" ~ "Snow petrel",
    TRUE ~ "Other"))

#Format phylogenetic tree
CommonNames <- unique(dd[c("Species", "CommonName")])
CommonNames$NewTipLabels <- paste(CommonNames$CommonName, " (", CommonNames$Species, ")", sep = "")
PhyloForPlot <- PhyloBrLen
PhyloForPlot$tip.label <- CommonNames$NewTipLabels[match(gsub("_", " ",PhyloBrLen$tip.label), CommonNames$Species)]
plot(PhyloForPlot)

#Data frame for plotting
CommonNames <- CommonNames[order(CommonNames$Species),]
Zrs <- MSp$b[1:13]
SpLower <- MSp$ci.lb[1:13]
SpUpper <- MSp$ci.ub[1:13]
SpDF <- data.frame(CommonNames$NewTipLabels,Zrs,SpLower,SpUpper, row.names = NULL)
SpDF$CommonNames.NewTipLabels <- factor(SpDF$CommonNames.NewTipLabels)

#Coloured tree (%<+% from ggtree)
tree <- ggtree(PhyloForPlot, ladderize = FALSE, size = 1.5, aes(color = Zrs)) %<+% SpDF +
  scale_color_continuous(low="darkslategrey", high="palegreen",
                         breaks = c(-0.7, -0.5, -0.25, 0, 0.25)) + 
  geom_tiplab(as_ylab=TRUE) +
  theme(legend.position="bottom",
        axis.text.y = element_text(size = 12, colour = "black")) +
  guides(color = guide_colorbar(title = "Zr", title.position = "left", title.vjust = 0.9)) +
  theme(legend.direction = "horizontal",
        legend.position = "bottom",
        legend.key.height = unit(0.5, "cm"),
        legend.key.width = unit(1.5, "cm")) 
tree
ggsave(tree, filename = "Tree.svg",  bg = "white", width = 8, height = 5)
```

```{r}
#Forest plot
SpDF$CommonNames.NewTipLabels <- factor(SpDF$CommonNames.NewTipLabels,
                                        levels = rev(c("Sand lizard (Lacerta agilis)",
                                                   "Alpine swift (Tachymarptis melba)",
                                                   "Snow petrel (Pagodroma nivea)",
                                                   "European shag (Gulosus aristotelis)",
                                                   "Common tern (Sterna hirundo)",
                                                   "Western jackdaw (Corvus monedula)",
                                                   "Seychelles warbler (Acrocephalus sechellensis)",
                                                   "Great reed warbler (Acrocephalus arundinaceus)",
                                                   "House sparrow (Passer domesticus)",
                                                   "White-browed sparrow-weaver (Plocepasser mahali)",
                                                   "European badger (Meles meles)",
                                                   "Domestic sheep (Ovis aries)",
                                                   "Human (Homo sapiens)")))

SpForest <- ggplot(data = SpDF,
                   aes(x = CommonNames.NewTipLabels, y = Zrs, ymin = SpLower, ymax = SpUpper)) +
  geom_pointrange(linewidth = 0.25, fatten = 5, shape=15) + 
  geom_hline(yintercept = 0, lty = 2) +
  geom_hline(yintercept = -0.0682, lty = 1) + # -0.0682 is mean-adjusted Zr like in histogram
  coord_flip() +  # flip coordinates (puts labels on y axis)
  scale_y_continuous(limits = c(-1,1), breaks = seq(-1, 1, by = 0.25)) +
  ylab("Zr (95% CI)") +
  theme(panel.background = element_rect(fill = "transparent"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        plot.background = element_rect(fill = "transparent"),
        axis.title.y = element_blank(),
        axis.title.x = element_text(colour = "black", margin = margin(t = 20)),
        axis.line.x = element_line(colour = "black"),
        axis.text.x = element_text(colour = "black"),
        axis.line.y = element_blank(),
        axis.text.y = element_blank(), # don't display species names
        axis.ticks.y = element_blank())
SpForest
ggsave(SpForest, filename = "SpForest.svg",  bg = "transparent", width = 4, height = 4)
```

```{r}
#svglite::svglite(filename="Tree-SpForest.svg", width = 12, height = 5, pointsize = 12, bg = "transparent")
#ggarrange(tree, SpForest, ncol = 2, nrow = 1, widths = c(2,1), align = "h")
#dev.off()

Tree_SpForest <- ggarrange(tree, SpForest, ncol = 2, align = "v", heights = c(1, 1))
ggsave("Tree-SpForest.svg", Tree_SpForest, width = 45, height = 15, units = "cm")
```
## M1. All random effects to account for non-independence among studies but no moderators yet

### Phylogeny
```{r message=FALSE, warning=FALSE}
#Phylogeny
#Get phyl names from species
Names <- tnrs_match_names(dd$Species) # "rotl"

# Construct phylogenetic tree
Phylo <- tol_induced_subtree(ott_ids = Names$ott_id, label_format = "name") # "rotl"
plot(Phylo, no.margin = TRUE)
save(Phylo, file = "PhyloNew.Rdata")

# Create phylogenetic variance-covariance matrix
PhyloBrLen <- compute.brlen(Phylo) # "ape"
PhyloMatrix <- vcv(PhyloBrLen, corr = TRUE)
save(PhyloMatrix, file = "PhyloMatrixNew.Rdata")
#load("~/meta/code/project/PhyloMatrixNew.Rdata")
```

```{r,echo=T}
m1 <- rma.mv(Zr, ZrVar, random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny),
                 R = list(Phylogeny = PhyloMatrix),
                 data = dd, method = "ML")
summary(m1)
tidy(m1, conf.int = T)
```

### Check whether random effects are normally distributed through Q-Q plot for residuals

```{r}
residuals <- residuals(m1)
fitted <- fitted(m1)
qqnorm(residuals, main = "Q-Q Plot of Residuals")
qqline(residuals, col = "red")
```

### Get LRT of each random effect by comparing reduced model to full model with anova

```{r}
LRT_study = rma.mv(Zr,ZrVar, random = list(~1|EstimateID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd)
LRT_estimate = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd)
LRT_phylogeny = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|EstimateID),method = "ML", data = dd)

anova(m1, LRT_study) # 23.5825 (<0.0001)
anova(m1, LRT_estimate) # 219.2224 (<0.0001)
anova(m1, LRT_phylogeny) # 13.0762 (0.0003)
```

Large LRT with a small p-value: factor significantly contributes to the model, keep the it in the model.

### Test which random effects to add to the models by comparing AIC, BIC, logLik in all combinations of random effects

```{r}
re <- list(
st = rma.mv(Zr,ZrVar, random = ~1|StudyID, method = "ML", data = dd),
st.est = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|EstimateID),method = "ML", data = dd),
st.sp = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|Species),method = "ML", data = dd),
st.ph = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix),method = "ML", data = dd),
est = rma.mv(Zr,ZrVar, random = ~1|EstimateID,method = "ML", data = dd),
est.sp = rma.mv(Zr,ZrVar, random = list(~1|EstimateID, ~1|Species),method = "ML", data = dd),
est.ph = rma.mv(Zr,ZrVar, random = list(~1|EstimateID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd),
sp = rma.mv(Zr,ZrVar, random = ~1|Species,method = "ML", data = dd),
sp.ph = rma.mv(Zr,ZrVar, random = list(~1|Species, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix),method = "ML", data = dd),
ph = rma.mv(Zr,ZrVar, random = ~1|Phylogeny,R = list(Phylogeny = PhyloMatrix),method = "ML", data = dd),
st.est.sp = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|EstimateID, ~1|Species), method = "ML", data = dd),
st.sp.ph = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|Species, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd),
st.est.ph = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd),
sp.est.ph = rma.mv(Zr,ZrVar, random = list(~1|Species, ~1|EstimateID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd),
st.est.sp.ph = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|EstimateID, ~1|Species, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix),method = "ML", data = dd))

#Model comparison
random_eff <- data.frame(AIC = sapply(re, AIC),
                         BIC = sapply(re, BIC),
                         logLik = sapply(re, logLik))
random_eff[order(random_eff$AIC), ]
```

est.sp, est.ph, st.est.sp, st.est.ph, sp.est.ph, st.est.sp.ph AIC values are good. I will be using st.est.ph in the meta-regression to account for all random effects, as they are all important for the study question

### Variance components for each random effect [sigma\^2], 95% confidence intervals (CIs) + proportion heterogeneity each variance component explains

Lower bound of the variance estimates cannot be negative since variance (sigma\^2) must always be zero or positive. So if CI includes zero, it means the variance component is not significantly different from zero + little evidence for variability among the estimates

```{r}
confint_m1 <- confint(m1)
confint_m1

#### From 10.1007/s10682-012-9555-5 and 10.1111/jeb.14071

wj <- 1/dd$ZrVar # wj is weight (inverse of sampling variance) of jth size
s2m <- sum(wj)*(length(unique(dd$StudyID)-1))/((sum(wj))^2-sum(wj^2)) #s2m is within-study variance, typical sampling error
m1.s2t <- sum(m1$sigma2)+s2m #Total variance, eq23

m1I2total <- sum(m1$sigma2)/m1.s2t #I\^2 total: 0.9963593738
m1I2Study <- m1$sigma2[1]/m1.s2t # I\^2 for StudyID: 0.1517161853
m1I2Estimate <- m1$sigma2[2]/m1.s2t # I\^2 for EstimateID: 0.06139386308
m1I2Phylogeny <- m1$sigma2[3]/m1.s2t # I\^2 for Phylogeny: 0.7832493717
m1I2Resid <- s2m/m1.s2t # I\^2 residual: 0.003640626207
```

### Subset into human and animal (all random effects)

Check if subgrouping by human/animal and including species as a random effect influences model fit for each group. This will show whether Species is relevant across groups or if the variance is mostly driven by one category (so from human studies)

```{r}
dd$SpeciesType <- ifelse(dd$Species == "Homo sapiens", "Human", "Animal")
dd$SpeciesType <- factor(dd$SpeciesType, levels = c("Human", "Animal"))

### --------------- HUMAN
m1_human <- rma.mv(Zr, ZrVar, random = list(~1|StudyID, ~1|EstimateID),
                  data = dd[dd$SpeciesType == "Human",], method = "ML")
summary(m1_human)
confint_m1_human <- confint(m1_human)
confint_m1_human
# Heterogeneity proportion

wj_m1_human <- 1/dd[dd$SpeciesType == "Human",]$ZrVar # wj is weight (inverse of sampling variance) of jth size
s2m_m1_human <- sum(wj_m1_human)*(length(unique(dd[dd$SpeciesType == "Human",]$StudyID)-1))/((sum(wj_m1_human))^2-sum(wj_m1_human^2)) #s2m is within-study variance, typical sampling error
m1_human.s2t <- sum(m1_human$sigma2)+s2m_m1_human # total variance
m1_humanI2total <- sum(m1_human$sigma2)/m1_human.s2t #0.9859336395
m1_humanI2Study <- m1_human$sigma2[1]/m1_human.s2t #0.6504705178
m1_humanI2Estimate <- m1_human$sigma2[2]/m1_human.s2t #0.3354631217
m1_humanI2Resid <- s2m/m1_human.s2t #0.01711328843

LRT_study_human = rma.mv(Zr,ZrVar, random = ~1|StudyID, method = "ML", data = dd[dd$SpeciesType == "Human",])
LRT_estimate_human = rma.mv(Zr,ZrVar, random = ~1|EstimateID, method = "ML", data = dd[dd$SpeciesType == "Human",])
anova(m1_human, LRT_study_human) # LRT for StudyID - 205.3071
anova(m1_human, LRT_estimate_human) # LRT for EstimateID - 16.6789

### --------------- ANIMAL
m1_animal <- rma.mv(Zr, ZrVar, random = list(~1|StudyID,~1|EstimateID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd[dd$SpeciesType == "Animal",],)
summary(m1_animal)
confint_m1_animal <- confint(m1_animal)
confint_m1_animal

# Heterogeneity proportion

wj_m1_animal <- 1/dd[dd$SpeciesType == "Animal",]$ZrVar # wj is weight (inverse of sampling variance) of jth size
s2m_m1_animal <- sum(wj_m1_animal)*(length(unique(dd[dd$SpeciesType == "Animal",]$StudyID)-1))/((sum(wj_m1_animal))^2-sum(wj_m1_animal^2)) #s2m is within-study variance, typical sampling error
m1_animal.s2t <- sum(m1_animal$sigma2)+s2m_m1_animal # total variance
m1_animalI2total <- sum(m1_animal$sigma2)/m1_animal.s2t # 0.9898225701
m1_animalI2Study <- m1_animal$sigma2[1]/m1_animal.s2t # 0.1940391349
m1_animalI2Estimate <- m1_animal$sigma2[2]/m1_animal.s2t # 0.04254666871
m1_animalI2Phylogeny <- m1_animal$sigma2[3]/m1_animal.s2t # 0.7532367665
m1_animalI2Resid <- s2m/m1_animal.s2t #0.003743250647

LRT_study_animal = rma.mv(Zr,ZrVar, random = list(~1|EstimateID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd[dd$SpeciesType == "Animal",],)
LRT_estimate_animal = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix),method = "ML", data = dd[dd$SpeciesType == "Animal",],)
LRT_phylogeny_animal = rma.mv(Zr,ZrVar, random = list(~1|StudyID, ~1|EstimateID), method = "ML", data = dd[dd$SpeciesType == "Animal",],)

anova(m1_animal, LRT_study_animal) # 0.7763 (0.3783)
anova(m1_animal, LRT_estimate_animal) # 14.7227 (0.0001)
anova(m1_animal, LRT_phylogeny_animal) # 0.3242 (0.5691)
```

#### Repeat forest plots with human/animal subroups

```{r}
par(tck=-0.01, mgp=c(2.5,0.5,0), mar=c(2,1,1,1))

# human individual estimates
m0_human <- rma(Zr,ZrVar, data = dd[dd$SpeciesType == "Human",], method = "ML", slab=paste(Author.s., sep=", "))
forest(m0_human,
       alim = c(-3,4), at=seq(-1,1, by=0.25), order="obs",
       efac=c(0,0,0), col="black", psize=0.75,
       cex=0.65,
       cex.lab=1, #x-axis title
       cex.axis=1, #x-axis labels
       lty=c("solid","blank"), # remove horizontal line at top of plot
       xlim=c(-2,1.5), # adjust horizontal plot region limits
       header="Author(s) and Year",
       shade="zebra")

# animal individual estimates
m0_animal <- rma(Zr,ZrVar, data = dd[dd$SpeciesType == "Animal",], method = "ML", slab=paste(Author.s., sep=", "))
forest(m0_animal,
       alim = c(-3,4), at=seq(-1,1, by=0.25), order="obs",
       efac=c(0,0,0), col="black", psize=0.75,
       cex=0.65,
       cex.lab=1, #x-axis title
       cex.axis=1, #x-axis labels
       lty=c("solid","blank"), # remove horizontal line at top of plot
       xlim=c(-2,1.5), # adjust horizontal plot region limits
       header="Author(s) and Year",
       shade="zebra")
```


```{r}
models <- list()
models[['Model 1']] <- m1
models[['Model 1 - human subset']] <- m1_human
models[['Model 1 - animal subset']] <- m1_animal

options(modelsummary_get = "broom")

m1summary = modelsummary(models, fmt = 4, shape = term ~ model + statistic,
                         stars = c("*" = 0.05, "**" = 0.01, "***" = 0.001), 
                         estimate = "{estimate} ({std.error})",
                         statistic = c("[{conf.low}, {conf.high}]", "{p.value} {stars}"),
                         gof_map = c("nobs", "aic","bic","logLik","aicc", "deviance", "df.residual")) |>
  setNames(c("", "estimate (SE)","95% CI","p-val","estimate (SE)","95% CI","p-val","estimate (SE)","95% CI","p-val"))
save_tt(m1summary, output = "m1summary.docx",overwrite=T)
```

# Meta-regression (by including moderators)

```{r}
#check multicollinearity by checking VIFs (variance inflation factors)
dd$Artif_Wild <- ifelse(dd$EnvCond == "Human" | dd$EnvCond == "Captive", "Artificial", "Wild")

viftest <- rma(Zr,ZrVar,
                mods = ~OffSex+ParSex+Artif_Wild+SpermProdSeason+EnvEff+MF_ID+W_B_PEff+OffAgeTL+MethFact+Tissue,
                data = dd)
vif.rma(viftest, table=T)
# Remove Artif_Wild as moderator (EnvCond combined)
```

## Model Selection

```{r}
## For some reason this works only on Windows
## https://gist.github.com/wviechtb/891483eea79da21d057e60fd1e28856b
## Model Selection using the glmulti and MuMIn Packages with a rma.mv() Model
############################################################################
##--------------------------------------------- MuMIn with parallel processing
## fit the full model (m2) (multilevel phylogenetic meta-analytic model)
# full = rma.mv(Zr,ZrVar, mods = ~OffSex+ParSex+SpermProdSeason+EnvEff+MF_ID+W_B_PEff+OffAgeTL+MethFact+Tissue,
#              random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny),
#              R = list(Phylogeny = PhyloMatrix),
#              method = "ML", data = dd, control = list(rel.tol = 1e-8))
# 
# num_cores <- detectCores()
# clust <- makeCluster(num_cores, type="PSOCK")
# clusterExport(clust, c("dd","PhyloMatrix"))
# clusterEvalQ(clust, library(metafor))
# 
# system.time(model_selection <- dredge(full, trace=2, cluster=clust))
# model_selection
# 
# stopCluster(clust)
```

## M2 insignificant interaction: all random effects/all moderators + interactions (parsex * offsex, tissue * offage)

```{r}
# Set reference levels
dd$W_B_PEff <- relevel(dd$W_B_PEff, ref = "Neither")
dd$ParSex <- relevel(dd$ParSex, ref = "F")
dd$OffSex <- relevel(dd$OffSex, ref = "F")
dd$Tissue <- relevel(dd$Tissue, ref = "Leucocytes")

m_temp <- rma.mv(Zr,ZrVar,
             mods = ~ ParSex*OffSex + Tissue*OffAgeTL + OffSex + ParSex+ SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue,
             random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny),
             R = list(Phylogeny = PhyloMatrix),
             method = "ML", data = dd, control = list(rel.tol = 1e-8))
summary(m_temp)
```

## M2 All random effects/all moderators + interactions (parsex * offsex)

```{r}
# Remove non-significant interaction (tissue * offage)
m2 <- rma.mv(Zr,ZrVar, mods = ~ParSex*OffSex + OffSex + ParSex+ SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue,
             random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny),
             R = list(Phylogeny = PhyloMatrix),
             method = "ML", data = dd, control = list(rel.tol = 1e-8), slab=paste(Author.s.))
summary(m2)

# Variance components for each random effect [sigma\^2]
confint_m2 <- confint(m2)
confint_m2
# 95% confidence intervals (CIs) + proportion heterogeneity each variance component explains
m2.s2t <- sum(m2$sigma2)+s2m # total variance
m2I2total <- sum(m2$sigma2)/m2.s2t
m2I2Study <- m2$sigma2[1]/m2.s2t
m2I2Estimate <- m2$sigma2[2]/m2.s2t
m2I2Phylogeny <- m2$sigma2[3]/m2.s2t
m2I2Resid <- s2m/m2.s2t 

# Marginal R^2 per factor with r2_ml  
R2_overall <- list(R2.ParSexOffSex <- rma.mv(Zr, ZrVar, mods = ~ParSex*OffSex, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.OffSex <- rma.mv(Zr, ZrVar, mods = ~OffSex, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.ParSex <- rma.mv(Zr, ZrVar, mods = ~ParSex, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.SpermProdSeason <- rma.mv(Zr, ZrVar, mods = ~SpermProdSeason, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.EnvEff <- rma.mv(Zr, ZrVar, mods = ~EnvEff, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.MF_ID <- rma.mv(Zr, ZrVar, mods = ~MF_ID, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.W_B_PEff <- rma.mv(Zr, ZrVar, mods = ~W_B_PEff, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.OffAgeTL <- rma.mv(Zr, ZrVar, mods = ~OffAgeTL, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.MethFact <- rma.mv(Zr, ZrVar, mods = ~MethFact, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.Tissue <- rma.mv(Zr, ZrVar, mods = ~Tissue, data = dd, method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)))

calc_R2 <- function(x) (round(R2_calc(x),7))
lapply(R2_overall, calc_R2)
```

### Subset into humans and animals

```{r}
dd_human <- dd[dd$SpeciesType == "Human", ]
dd_human$Tissue <- factor(relevel(dd_human$Tissue, ref = "Leucocytes"))

# Fisher's z transformed correlation coefficient histogram for human subset
histZr_human <- ggplot(data = dd_human, aes(x = Zr))+
  geom_histogram(binwidth = 0.05, colour = "black", fill = "grey90") +
  geom_vline(xintercept = mean(dd_human$Zr), linetype = "dashed", linewidth = 0.75, colour = "purple") +
  geom_vline(xintercept = 0.0949, linetype = "dashed", linewidth = 0.75, colour = "seagreen",show.legend=F) + #xintercept = 0.0949 is Zr adjusted for study, estimateID, phylogeny
  xlab("Fisher's z transformed correlation coefficient") +
  ylab("Frequency") +
  scale_x_continuous(breaks = seq(-1, 1, 0.1)) +
  scale_y_continuous(breaks = seq(0,40,5), limits = c(0,37), expand = c(0,0)) +
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
        
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        
        axis.ticks = element_line(colour = "black"),
        axis.line = element_line(colour = "black"),
        
        axis.text.x = element_text(size = 10,family = "Arial", colour = "black", margin=margin(t=5)),
        axis.text.y = element_text(size = 10, family = "Arial",colour = "black"),
        axis.title.x = element_text(size = 12, family = "Arial",colour = "black",margin=margin(t=10)),
        axis.title.y = element_text(size = 12, family = "Arial",colour = "black",margin=margin(r=10)))
histZr_human
ggsave(histZr_human, filename = "histZr_human.png", bg = "white", width=(20*(6/7)), height=(20*(3/7)), units = c("cm"))


m2_human <- rma.mv(Zr,ZrVar,
                   mods = ~ParSex*OffSex + OffSex + ParSex + EnvEff + MF_ID + OffAgeTL + MethFact + Tissue,
                   random = list(~1|StudyID, ~1|EstimateID),
                   method = "ML", data = dd_human, control = list(rel.tol = 1e-8))
summary(m2_human)

#orchard_plot(m2_human, mod = "OffAgeTL", group="StudyID", xlab = "Effect size (Zr)")
# Error in `contrasts<-`(`*tmp*`, value = contr.funs[1 + isOF[nn]]) : 
#  contrasts can be applied only to factors with 2 or more levels

# Variance components for each random effect [sigma\^2]
confint_m2_human <- confint(m2_human)
confint_m2_human
# 95% confidence intervals (CIs) + proportion heterogeneity each variance component explains
wj_m2_human <- 1/dd_human$ZrVar # wj is weight (inverse of sampling variance) of jth size
s2m_m2_human <- sum(wj_m2_human)*(length(unique(dd_human$StudyID)-1))/((sum(wj_m2_human))^2-sum(wj_m2_human^2)) #s2m is within-study variance, typical sampling error
m2_human.s2t <- sum(m2_human$sigma2)+s2m_m2_human # total variance
m2_humanI2total <- sum(m2_human$sigma2)/m2_human.s2t # 0.9509387436
m2_humanI2Study <- m2_human$sigma2[1]/m2_human.s2t # 0.1978028535
m2_humanI2Estimate <- m2_human$sigma2[2]/m2_human.s2t # 0.7531358902
m2_humanI2Resid <- s2m_m2_human/m2_human.s2t # 0.04906125638

# Marginal R^2 per factor with r2_ml  
R2_human <- list(R2.ParSexOffSex <- rma.mv(Zr, ZrVar, mods = ~ParSex*OffSex, data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)),
               
               R2.OffSex <- rma.mv(Zr, ZrVar, mods = ~OffSex,data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)),
               
               R2.ParSex <- rma.mv(Zr, ZrVar, mods = ~ParSex, data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)),
               
               R2.SpermProdSeason <- rma.mv(Zr, ZrVar, mods = ~SpermProdSeason, data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)),
               
               R2.EnvEff <- rma.mv(Zr, ZrVar, mods = ~EnvEff, data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)),
               
               R2.MF_ID <- rma.mv(Zr, ZrVar, mods = ~MF_ID, data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)),
               
               R2.W_B_PEff <- rma.mv(Zr, ZrVar, mods = ~W_B_PEff, data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)),
               
               R2.OffAgeTL <- rma.mv(Zr, ZrVar, mods = ~OffAgeTL, data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)),
               
               R2.MethFact <- rma.mv(Zr, ZrVar, mods = ~MethFact, data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)),
               
               R2.Tissue <- rma.mv(Zr, ZrVar, mods = ~Tissue, data = dd[dd$SpeciesType == "Human",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID)))

calc_R2 <- function(x) (round(R2_calc(x),7))
lapply(R2_human, calc_R2)

dd_animal <- dd[dd$SpeciesType == "Animal", ]
dd_animal$OffSex <- factor(relevel(dd_animal$OffSex, ref = "F"))
dd_animal$MethFact <- factor(relevel(dd_animal$MethFact, ref = "qPCR"))
dd_animal$Tissue <- factor(relevel(dd_animal$Tissue, ref = "Leucocytes"))

# Fisher's z transformed correlation coefficient histogram for animal subset
histZr_animal <- ggplot(data = dd_animal, aes(x = Zr))+
  geom_histogram(binwidth = 0.05, colour = "black", fill = "grey90") +
  geom_vline(xintercept = mean(dd_animal$Zr), linetype = "dashed", linewidth = 0.75, colour = "purple") +
  geom_vline(xintercept = -0.0865, linetype = "dashed", linewidth = 0.75, colour = "seagreen",show.legend=F) + #xintercept = -0.0865 is Zr adjusted for study, estimateID, phylogeny
  xlab("Fisher's z transformed correlation coefficient") +
  ylab("Frequency") +
  scale_x_continuous(breaks = seq(-1, 1, 0.1)) +
  scale_y_continuous(breaks = seq(0,40,5), limits = c(0,37), expand = c(0,0)) +
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
        
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        
        axis.ticks = element_line(colour = "black"),
        axis.line = element_line(colour = "black"),
        
        axis.text.x = element_text(size = 10,family = "Arial", colour = "black", margin=margin(t=5)),
        axis.text.y = element_text(size = 10, family = "Arial",colour = "black"),
        axis.title.x = element_text(size = 12, family = "Arial",colour = "black",margin=margin(t=10)),
        axis.title.y = element_text(size = 12, family = "Arial",colour = "black",margin=margin(r=10)))
histZr_animal
ggsave(histZr_animal, filename = "histZr_animal.png", bg = "white", width=(20*(6/7)), height=(20*(3/7)), units = c("cm"))


m2_animal <- rma.mv(Zr,ZrVar,
                   mods = ~ OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue,
             random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix),
             method = "ML", data = dd_animal, control = list(rel.tol = 1e-8))
summary(m2_animal)

orchard_plot(m2_animal, mod = "ParSex", group="StudyID", xlab = "Effect size (Zr)")


# Variance components for each random effect [sigma\^2]
confint_m2_animal <- confint(m2_animal)
confint_m2_animal
# 95% confidence intervals (CIs) + proportion heterogeneity each variance component explains
wj_m2_animal<- 1/dd_animal$ZrVar # wj is weight (inverse of sampling variance) of jth size
s2m_m2_animal <- sum(wj_m2_animal)*(length(unique(dd_animal$StudyID)-1))/((sum(wj_m2_animal))^2-sum(wj_m2_animal^2)) #s2m is within-study variance, typical sampling error

m2_animal.s2t <- sum(m2_animal$sigma2)+s2m_m2_animal # total variance
m2_animalI2total <- sum(m2_animal$sigma2)/m2_animal.s2t # 0.9137232861
m2_animalI2Study <- m2_animal$sigma2[1]/m2_animal.s2t # 0.7211508428
m2_animalI2Estimate <- m2_animal$sigma2[2]/m2_animal.s2t # 0.1925722508
m2_animalI2Phylogeny <- m2_animal$sigma2[3]/m2_animal.s2t # 0.0000001925104915
m2_animalI2Resid <- s2m_m2_animal/m2_animal.s2t # 0.08627671391

R2_animal <- list(R2.ParSexOffSex <- rma.mv(Zr, ZrVar, mods = ~ParSex*OffSex, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.OffSex <- rma.mv(Zr, ZrVar, mods = ~OffSex, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.ParSex <- rma.mv(Zr, ZrVar, mods = ~ParSex, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.SpermProdSeason <- rma.mv(Zr, ZrVar, mods = ~SpermProdSeason, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.EnvEff <- rma.mv(Zr, ZrVar, mods = ~EnvEff, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.MF_ID <- rma.mv(Zr, ZrVar, mods = ~MF_ID, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.W_B_PEff <- rma.mv(Zr, ZrVar, mods = ~W_B_PEff, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.OffAgeTL <- rma.mv(Zr, ZrVar, mods = ~OffAgeTL, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.MethFact <- rma.mv(Zr, ZrVar, mods = ~MethFact, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)),
               
               R2.Tissue <- rma.mv(Zr, ZrVar, mods = ~Tissue, data = dd[dd$SpeciesType == "Animal",], method = "ML",
               random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix)))

calc_R2 <- function(x) (round(R2_calc(x),7))
lapply(R2_animal, calc_R2)
```

### Save

```{r}
models <- list(m2, m2_human, m2_animal)

options(modelsummary_get = "broom")

m2summary = modelsummary(
  models, shape = term ~ model + statistic, fmt = fmt_sprintf("%.4f"),
  stars = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  estimate = "{estimate} ({std.error})",
  statistic = c("[{conf.low}, {conf.high}]", "{p.value} {stars}"),
  gof_map = c("nobs", "aic","bic","logLik","aicc", "deviance", "df.residual"))
m2summary
#save_tt(m2summary, output = "m2summary.docx",overwrite=T)
```

## Emmeans m2

```{r}
### create reference grid
emmprepm2 <- emmprep(m2, verbose=TRUE)
### separate for human and animal subsets
emmprepm2_human <- emmprep(m2_human, verbose=TRUE)
emmprepm2_animal <- emmprep(m2_animal, verbose=TRUE)

### Check what parental-offspring sex combinations are significantly different
### from each other
emm_m2_human_SexInteraction <- emmeans(emmprepm2_human, ~ ParSex*OffSex)
pairs(emm_m2_human_SexInteraction)
HumanSexInteraction_pairs <- as.data.frame(pairs(emm_m2_human_SexInteraction))
write.xlsx(HumanSexInteraction_pairs, "SexCombination_posthoc.xlsx")
pairs_sig <- HumanSexInteraction_pairs%>%filter(p.value<0.05)

### Check whether lab method levels are different from each other
emm_m2_human_MethFact <- emmeans(emmprepm2_human, ~ MethFact)
pairs(emm_m2_human_MethFact)
emm_m2_animal_MethFact <- emmeans(emmprepm2_animal, ~ MethFact)
pairs(emm_m2_animal_MethFact)
### create dataframes for plotting
plot_human_MethFact <- tidy(emm_m2_human_MethFact, conf.int = TRUE)
plot_animal_MethFact <- tidy(emm_m2_animal_MethFact, conf.int = TRUE)

### Plot
human_MethFact <- ggplot(plot_human_MethFact, aes(x = MethFact, y = estimate)) +
  geom_bar(stat = "identity", color = "black", fill = "gray", width = 0.6) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                width = 0.2) +
  theme_classic() + 
  labs(x = "Laboratory method", y = "Estimate", title = "") +
  scale_x_discrete(labels = c("TRFInGel" = "TRF in-gel", "TRFSouthern" = "TRF Southern")) +
  geom_signif(comparisons = list(c("qPCR", "TRFInGel"), c("qPCR", "TRFSouthern"), 
                                 c("TRFInGel", "TRFSouthern"), 
                                 c("TRFInGel", "WGS")),
              annotations = c("***", "*", "***", "***"),
              y_position = c(0.65, 0.75, 0.85, 0.95), 
              tip_length = 0.03,
              textsize = 4,
              vjust = 0.5)
human_MethFact
animal_MethFact <- ggplot(plot_animal_MethFact, aes(x = MethFact, y = estimate)) +
  geom_bar(stat = "identity", color = "black", fill = "gray", width = 0.6) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                width = 0.2) +
  theme_classic() + 
  labs(x = "Laboratory method", y = "Estimate", title = "") +
  scale_x_discrete(labels = c("TRFInGel" = "TRF in-gel", "TRFSouthern" = "TRF Southern")) +
  geom_signif(comparisons = list(c("qPCR", "TRFSouthern")),
              annotations = c("**"),
              y_position = c(0.1),
              tip_length = 0.03,
              textsize = 4,
              vjust = 0.5)
animal_MethFact
### To combine to two plots, set the y-axis scale
y_limit <- c(-1.1, 1.1)
### A bit edition
human_MethFact <- human_MethFact + ylim(y_limit) + 
  ggtitle("Human") + theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))
animal_MethFact <- animal_MethFact + ylim(y_limit) +
  ggtitle("Non-human") + theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))
### Combine the plots
combined_plot <- (human_MethFact + animal_MethFact) + 
  plot_layout(ncol = 2) + 
  theme(plot.margin = margin(10, 10, 10, 10)) 
combined_plot
### Save
ggsave(combined_plot, filename = "LabMethod.png", bg = "white", width=16, height=12, units = c("cm"))

# ### estimated marginal mean using default equal cell weighting
# emmeans(emmprepm2,
#         specs="1", #In the special case where the mean (or weighted mean) of all the predictions is desired, specify specs as ~ 1 or "1".
#         type="response",
#         weights="proportional" #Weight in proportion to the frequencies (in the original data) of the factor combinations that are averaged over
#         )
# 
# emm_m2 <- tidy(emmprepm2)
# write.csv(emm_m2, "emm_m2.csv", row.names = FALSE)
```

## Orchard plot humans

```{r}
plotdf_human <- dd_human %>%
  mutate(ParSex = factor(recode(ParSex, "F"="Mother","M"="Father"), levels = c("Mother", "Father")),
         OffSex = factor(recode(OffSex, "F"="Daughter","M"="Son","Both"="Unspecified"), levels = c("Daughter", "Son","Unspecified")),
         SpermProdSeason = factor(SpermProdSeason, levels = c("Seasonal", "Continuous")),
         MethFact = factor(recode(MethFact, "qPCR"=" qPCR","TRFSouthern"="TRF-SB","TRFInGel"="TRF-in-gel", "WGS"="WGS"), levels = c(" qPCR","TRF-SB","TRF-in-gel","WGS")),
         OffAgeTL = factor(OffAgeTL, levels = c("Adult", "Juvenile","Both")),
         Tissue = factor(recode(Tissue, "Leucocytes"="Leucocytes"), levels = c("Leucocytes", "Other")),
         W_B_PEff = factor(W_B_PEff, levels = c("Within", "Between", "Neither")),
         EnvEff = factor(recode(EnvEff,"Yes"="Accounted","No"="Not accounted"),levels = c("Accounted", "Not accounted")),
         MF_ID = factor(recode(MF_ID,"Yes"="Accounted","No"="Not accounted"), levels = c("Accounted", "Not accounted")))

# # Define reference levels
# plotdf_human$W_B_PEff <- relevel(plotdf_human$W_B_PEff, ref = "Neither")
# plotdf_human$ParSex <- relevel(plotdf_human$ParSex, ref = "Female")
# plotdf_human$OffSex <- relevel(plotdf_human$OffSex, ref = "Female")
# plotdf_human$EnvEff <- relevel(plotdf_human$EnvEff, ref = "Not accounted")
# plotdf_human$MF_ID <- relevel(plotdf_human$MF_ID, ref = "Not accounted")
# plotdf_human$OffAgeTL <- relevel(plotdf_human$OffAgeTL, ref = "Adult")
# plotdf_human$MethFact <- relevel(plotdf_human$MethFact, ref = "qPCR")
# plotdf_human$Tissue <- relevel(plotdf_human$Tissue, ref = "Leukocytes")

m2plot_human <- rma.mv(Zr,ZrVar,
                   mods = ~ParSex*OffSex + OffSex + ParSex + EnvEff + MF_ID + OffAgeTL + MethFact + Tissue,
                   random = list(~1|StudyID, ~1|EstimateID),
                   method = "ML", data = plotdf_human, control = list(rel.tol = 1e-8))
summary(m2plot_human)

# m2humanOffSex <- orchard_plot(m2plot_human, mod="OffSex", group="StudyID", xlab = "Zr",transfm = c("none")) +
#   ggtitle("offspring sex") +
#   theme(plot.title = element_text(hjust = 0.5))
# m2humanOffSex
# 
# m2humanParSex <- orchard_plot(m2plot_human, mod="ParSex", group="StudyID", xlab = "Zr",transfm = c("none")) +
#   ggtitle("parental sex") +
#   theme(plot.title = element_text(hjust = 0.5))

m2humanParOffSex_prep <- mod_results(m2plot_human, mod = "OffSex", group = "StudyID", 
    by = "ParSex")
m2humanParOffSex <- orchard_plot(m2humanParOffSex_prep, mod="OffSex", group="StudyID", xlab = "Zr", transfm = c("none")) +
  xlab("Offspring sex") +
  ggtitle("Parental sex : Offspring sex") +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = c(0.9, 0.04)) +
  guides(size = "none",
         shape = guide_legend(title = "Parental sex"))

m2humanMethFact  <- orchard_plot(m2plot_human, mod="MethFact", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Laboratory method") +
  theme(plot.title = element_text(hjust = 0.5))

m2humanOffAgeTL <- orchard_plot(m2plot_human, mod="OffAgeTL", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Offspring age") +
  theme(plot.title = element_text(hjust = 0.5))

m2humanTissue <- orchard_plot(m2plot_human, mod="Tissue", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Cell type") +
  theme(plot.title = element_text(hjust = 0.5))

m2humanEnvEff <- orchard_plot(m2plot_human, mod="EnvEff", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Parental environment effect") +
  theme(plot.title = element_text(hjust = 0.5))

m2humanMF_ID <- orchard_plot(m2plot_human, mod="MF_ID", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Parent's identity controlled for") +
  theme(plot.title = element_text(hjust = 0.5))

HumanOrchards <- ggarrange(m2humanParOffSex,m2humanMethFact,m2humanOffAgeTL,m2humanTissue,m2humanEnvEff,m2humanMF_ID, ncol = 3, nrow = 2, labels = "auto")
HumanOrchards

#ggsave("HumanOrchards.png", plot = HumanOrchards, width = 12, height = 8, dpi = 300)
ggsave("HumanOrchards.svg", plot = HumanOrchards, width = 12, height = 8, dpi = 300)
```

## Orchard plot animals

```{r}
plotdf_animal <- dd_animal %>%
  mutate(ParSex = factor(recode(ParSex, "F"="Mother","M"="Father"), levels = c("Mother", "Father")),
         OffSex = factor(recode(OffSex, "F"="Daughter","M"="Son","Both"="Unspecified"), levels = c("Daughter", "Son","Unspecified")),
         SpermProdSeason = factor(SpermProdSeason, levels = c("Seasonal", "Continuous")),
         MethFact = factor(recode(MethFact, "qPCR"=" qPCR","TRFSouthern"="TRF-SB","TRFInGel"="TRF-in-gel", "WGS"="WGS"), levels = c(" qPCR","TRF-SB","TRF-in-gel","WGS")),
         OffAgeTL = factor(OffAgeTL, levels = c("Adult", "Juvenile","Both")),
         Tissue = factor(recode(Tissue, "Leucocytes"="Leucocytes", "Erythrocytes"="Erythrocytes"), levels = c("Leucocytes", "Erythrocytes", "Other")),
         W_B_PEff = factor(W_B_PEff, levels = c("Within", "Between", "Neither")),
         EnvEff = factor(recode(EnvEff,"Yes"="Accounted","No"="Not accounted"),levels = c("Accounted", "Not accounted")),
         MF_ID = factor(recode(MF_ID,"Yes"="Accounted","No"="Not accounted"), levels = c("Accounted", "Not accounted")))

# plotdf_animal$W_B_PEff <- relevel(plotdf_animal$W_B_PEff, ref = "Neither")
# plotdf_animal$ParSex <- relevel(plotdf_animal$ParSex, ref = "Female")
# plotdf_animal$OffSex <- relevel(plotdf_animal$OffSex, ref = "Female")

m2plot_animal <- rma.mv(Zr,ZrVar,
                   mods = ~ OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue,
             random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix),
             method = "ML", data = plotdf_animal, control = list(rel.tol = 1e-8))
summary(m2plot_animal)

# m2animalOffSex <- orchard_plot(m2plot_animal, mod="OffSex", group="StudyID", xlab = "Zr",transfm = c("none")) +
#   ggtitle("offspring sex") +
#   theme(plot.title = element_text(hjust = 0.5))
# m2animalOffSex
# 
# m2animalParSex <- orchard_plot(m2plot_animal, mod="ParSex", group="StudyID", xlab = "Zr",transfm = c("none")) +
#   ggtitle("parental sex") +
#   theme(plot.title = element_text(hjust = 0.5))
# m2animalParSex

m2animalParOffSex_prep <- mod_results(m2plot_animal, mod = "OffSex", group = "StudyID", 
    by = "ParSex")
m2animalParOffSex <- orchard_plot(m2animalParOffSex_prep, mod="OffSex", group="StudyID", xlab = "Zr", transfm = c("none")) +
  xlab("Offspring sex") +
  ggtitle("Parental sex : Offspring sex") +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = c(0.9, 0.04)) +
  guides(size = "none",
         shape = guide_legend(title = "Parental sex"))

m2animalSpermProdSeason <- orchard_plot(m2plot_animal, mod="SpermProdSeason", group="StudyID", xlab = "Zr") +
  ggtitle("Sperm seasonality") +
  theme(plot.title = element_text(hjust = 0.5))

m2animalMethFact  <- orchard_plot(m2plot_animal, mod="MethFact", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Laboratory method") +
  theme(plot.title = element_text(hjust = 0.5))

m2animalOffAgeTL <- orchard_plot(m2plot_animal, mod="OffAgeTL", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Offspring age") +
  theme(plot.title = element_text(hjust = 0.5))

m2animalTissue <- orchard_plot(m2plot_animal, mod="Tissue", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Cell type") +
  theme(plot.title = element_text(hjust = 0.5))

m2animalEnvEff <- orchard_plot(m2plot_animal, mod="EnvEff", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Parental environment effect") +
  theme(plot.title = element_text(hjust = 0.5))

m2animalMF_ID <- orchard_plot(m2plot_animal, mod="MF_ID", group="StudyID", xlab = "Zr",transfm = c("none")) +
  ggtitle("Parent's identity controlled for") +
  theme(plot.title = element_text(hjust = 0.5))

m2animalW_B_PEff <- orchard_plot(m2plot_animal, mod="W_B_PEff", group="StudyID", xlab = "Zr") +
  ggtitle("Within/between-parents effect") +
  theme(plot.title = element_text(hjust = 0.5))

AnimalOrchards <- ggarrange(m2animalParOffSex,m2animalSpermProdSeason, m2animalMethFact,m2animalOffAgeTL,m2animalTissue,m2animalEnvEff,m2animalMF_ID, m2animalW_B_PEff, ncol = 3, nrow = 3, labels = "auto")
AnimalOrchards

#ggsave("AnimalOrchards.png", plot = AnimalOrchards, width = 12, height = 12, dpi = 300)
ggsave("AnimalOrchards.svg", plot = AnimalOrchards, width = 12, height = 12, dpi = 300)
```


### Subset into humans and animals

```{r}
m3_human <- rma.mv(Zr,ZrVar,
             mods = ~ParSex*OffSex + Tissue*OffAgeTL + SpermProdSeason+EnvEff + EnvCond + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue,
             random = list(~1|StudyID, ~1|EstimateID),
             method = "ML", data = dd[dd$SpeciesType == "Human",], control = list(rel.tol = 1e-8))
# performance::model_performance(m3_human, metrics="all")
m3_human_summary <- tidy(m3_human, conf.int = T)

m3_animal <- rma.mv(Zr,ZrVar,
             mods = ~ParSex*OffSex + Tissue*OffAgeTL + SpermProdSeason+EnvEff + EnvCond + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue,
             random = list(~1|StudyID, ~1|Species, ~1|EstimateID),
             method = "ML", data = dd[dd$SpeciesType == "Animal",], control = list(rel.tol = 1e-8))
#performance::model_performance(m3_animal, metrics="all")
m3_animal_summary <- tidy(m3_animal, conf.int = T)
```

#### Relevel

```{r}
# releveled to male "M" offspring
dd$OffSex <- relevel(dd$OffSex, ref = "M")
m3M <- rma.mv(Zr,ZrVar,
             mods = ~OffSex+ParSex+SpermProdSeason+EnvEff+EnvCond+MF_ID+W_B_PEff+OffAgeTL+MethFact+Tissue,
             random = list(~1|StudyID, ~1|EstimateID, ~1|Species, ~1|Phylogeny),
             R = list(Phylogeny = PhyloMatrix),
             method = "ML", data = dd, control = list(rel.tol = 1e-8), slab=paste(Author.s.))
m3M_human <- rma.mv(Zr,ZrVar,
             mods = ~OffSex+ParSex+SpermProdSeason+EnvEff+EnvCond+MF_ID+W_B_PEff+OffAgeTL+MethFact+Tissue,
             random = list(~1|StudyID, ~1|EstimateID),
             method = "ML", data = dd[dd$SpeciesType == "Human",], control = list(rel.tol = 1e-8))
m3M_animal <- rma.mv(Zr,ZrVar,
             mods = ~OffSex+ParSex+SpermProdSeason+EnvEff+EnvCond+MF_ID+W_B_PEff+OffAgeTL+MethFact+Tissue,
             random = list(~1|StudyID, ~1|Species, ~1|EstimateID),
             method = "ML", data = dd[dd$SpeciesType == "Animal",], control = list(rel.tol = 1e-8))

# releveled to "Both" offspring
dd$OffSex <- relevel(dd$OffSex, ref = "Both")
m3B <- rma.mv(Zr,ZrVar,
             mods = ~OffSex+ParSex+SpermProdSeason+EnvEff+EnvCond+MF_ID+W_B_PEff+OffAgeTL+MethFact+Tissue,
             random = list(~1|StudyID, ~1|EstimateID, ~1|Species, ~1|Phylogeny),
             R = list(Phylogeny = PhyloMatrix),
             method = "ML", data = dd, control = list(rel.tol = 1e-8), slab=paste(Author.s.))
m3B_human <- rma.mv(Zr,ZrVar,
             mods = ~OffSex+ParSex+SpermProdSeason+EnvEff+EnvCond+MF_ID+W_B_PEff+OffAgeTL+MethFact+Tissue,
             random = list(~1|StudyID, ~1|EstimateID),
             method = "ML", data = dd[dd$SpeciesType == "Human",], control = list(rel.tol = 1e-8))
m3B_animal <- rma.mv(Zr,ZrVar,
             mods = ~OffSex+ParSex+SpermProdSeason+EnvEff+EnvCond+MF_ID+W_B_PEff+OffAgeTL+MethFact+Tissue,
             random = list(~1|StudyID, ~1|Species, ~1|EstimateID),
             method = "ML", data = dd[dd$SpeciesType == "Animal",], control = list(rel.tol = 1e-8))

m3M_summary <- tidy(m3M, conf.int = T)
m3M_human_summary <- tidy(m3M_human, conf.int = T)
m3M_animal_summary <- tidy(m3M_animal, conf.int = T)
m3B_summary <- tidy(m3B, conf.int = T)
m3B_human_summary <- tidy(m3B_human, conf.int = T)
m3B_animal_summary <- tidy(m3B_animal, conf.int = T)
```

# Publication and time-lag biases

## Funnel plot

Using residuals from m2

```{r}
svglite::svglite(filename="funnel.svg", width = 7, height = 5, pointsize = 12, bg = "white")

funnel(m2, yaxis="seinv", #inverse of the standard errors
       level = c(90, 95, 99), shade = c("white", "gray55", "gray75"), back = "white",
       digits = 1L,
       xlim = c(-1,1), ylim = c(2.5, 12.5), steps = 5, 
       refline = 0,
       legend = list(x = "topright",show = "cis",cex = 0.7), cex = 0.35,
       xlab = "Residual Zr",
       ylab = "Precision (inverse of standard error)")
dev.off() 
```

Split by humans and animals (residuals from m2)

```{r}
# Both on one plot

SpeciesCol <- c("green2", "purple")[dd$SpeciesType]

svglite::svglite(filename="funnel_split.svg", width = 7, height = 5, pointsize = 12, bg = "white")
funnel(m2, yaxis="seinv", 
       level = c(90, 95, 99), shade = c("white", "gray55", "gray75"),
       back = "white", col = SpeciesCol,
       digits = 1L, xlim = c(-1,1), ylim = c(2.5, 12.5), steps = 5, 
       refline = 0, # or adjusted mean Zr from the model?
       legend = list(x = "topright", show = "cis", cex = 0.7),
       cex = 0.35, xlab = "Residual Zr", ylab = "Precision (inverse of standard error)")
dev.off() 

# Humans

svglite::svglite(filename="funnel_humans.svg", width = 7, height = 5, pointsize = 12, bg = "white")
funnel(m2_human, yaxis="seinv", 
       level = c(90, 95, 99), shade = c("white", "gray55", "gray75"),
       back = "white",
       digits = 1L, xlim = c(-1,1), ylim = c(2.5, 30), steps = 12,
       refline = 0, # or adjusted mean Zr from the model?
       legend = list(x = "topright", show = "cis", cex = 0.7),
       cex = 0.35, xlab = "Residual Zr", ylab = "Precision (inverse of standard error)")
mtext("A) Human subset", side = 3, adj = 0, line = 1, font = 1)
dev.off() 

# Animals
svglite::svglite(filename="funnel_animals.svg", width = 7, height = 5, pointsize = 12, bg = "white")
funnel(m2_animal, yaxis="seinv", 
       level = c(90, 95, 99), shade = c("white", "gray55", "gray75"),
       back = "white",
       digits = 1L, xlim = c(-1,1), ylim = c(2.5, 30), steps = 12, 
       refline = 0, # or adjusted mean Zr from the model?
       legend = list(x = "topright", show = "cis", cex = 0.7),
       cex = 0.35, xlab = "Residual Zr", ylab = "Precision (inverse of standard error)")
mtext("B) Non-human subset", side = 3, adj = 0, line = 1, font = 1)
dev.off() 
```

## Egger's test

To statistically test for asymmetry, adding random effects to account for non-independence among estimates using sampling variance for publication bias and centered year for time-lag

```{r}
# Overall
m.pubbias <- rma.mv(Zr,ZrVar,
                    mods = ~ZrVar + year.c + ParSex*OffSex + OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd)
#m.pubbias

m.pubbias.human <- rma.mv(Zr,ZrVar,
             mods = ~ZrVar + year.c + ParSex*OffSex + OffSex + ParSex + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue,
             random = list(~1|StudyID, ~1|EstimateID),
             method = "ML", data = dd[dd$SpeciesType == "Human",], control = list(rel.tol = 1e-8))
m.pubbias.human

m.pubbias.animal <- rma.mv(Zr,ZrVar,
             mods = ~ZrVar + year.c + ParSex*OffSex + OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd[dd$SpeciesType == "Animal",], control = list(rel.tol = 1e-8))
m.pubbias.animal
```

# Plot figures

## Moderators

```{r}

### Overall

plotdf <- dd %>%
  mutate(ParSex = factor(recode(ParSex, "F"="Female","M"="Male"), levels = c("Female", "Male")),
         OffSex = factor(recode(OffSex, "F"="Female","M"="Male","Both"="Unspecified"), levels = c("Female", "Male","Unspecified")),
         SpermProdSeason = factor(SpermProdSeason, levels = c("Seasonal", "Continuous")),
         MethFact = factor(recode(MethFact, "qPCR"="qPCR","TRFSouthern"="TRF-SB","TRFInGel"="TRF-IG", "WGS"="WGS"), levels = c("qPCR","TRF-SB","TRF-IG","WGS")),
         OffAgeTL = factor(OffAgeTL, levels = c("Adult", "Juvenile","Both")),
         Tissue = factor(Tissue, levels = c("Leucocytes","Erythrocytes","Other")),
        # EnvCond = factor(EnvCond, levels = c("Wild", "Human")),
         W_B_PEff = factor(W_B_PEff, levels = c("Within", "Between", "Neither")),
         EnvEff = factor(recode(EnvEff,"Yes"="Accounted","No"="Not accounted"),levels = c("Accounted", "Not accounted")),
         MF_ID = factor(recode(MF_ID,"Yes"="Accounted","No"="Not accounted"), levels = c("Accounted", "Not accounted")))

# Unified moderators/fixed effects plot with facet_wrap
plotdf_long <- plotdf %>% pivot_longer(cols = c(MethFact, Tissue, SpermProdSeason, OffSex, OffAgeTL, ParSex, EnvEff, W_B_PEff, MF_ID), names_to = "Category", values_to = "Value") %>% mutate(Category = factor(Category, levels = c("ParSex","OffSex","SpermProdSeason","Tissue","OffAgeTL","MethFact","W_B_PEff","EnvEff","MF_ID"))) %>% mutate(Value = factor(Value))

meta_theme <- list(theme(panel.background = element_blank(),
                         panel.grid.major = element_blank(),
                         panel.grid.minor = element_blank(),
                         panel.border = element_rect(colour = "black", fill=NA, size=1),
                         axis.ticks = element_line(colour = "black"),
                         axis.text.x = element_text(size = 10, colour = "black", margin = margin(t = 5)),
                         axis.text.y = element_text(size = 10, colour = "black"),
                         axis.title.x = element_text(size = 12, colour = "black", margin = margin(t = 20)), 
                         axis.title.y = element_text(size = 12, colour = "black", margin = margin(r = 5))), 
                         #axis.line = element_line(colour = "black"),
                   geom_bar(stat = "count", width = 0.5, colour = "black", fill = "grey75"),
                   geom_text(aes(label = after_stat(count)), stat = "count", size = 3, vjust = -0.5),
                   scale_y_continuous(breaks = seq(0,140,20), limits = c(0,145), expand = c(0,0)),
                   ylab("Frequency"))

faceted_moderators_comb_plot <- ggplot(plotdf_long, aes(x = Value)) +
  facet_wrap(~ Category,
             labeller = labeller(Category = c("ParSex" = "(a) Parental sex",
                                              "OffSex" = "(b) Offspring sex",
                                              "SpermProdSeason" = "(c) Sperm production seasonality",
                                              "Tissue" = "(d) Cell type",
                                              "OffAgeTL" = "(e) Offspring age at measurement",
                                              "MethFact" = "(f) Laboratory method",
                                              "W_B_PEff" = "(g) Within-/between-parent effects",
                                              "EnvEff" = "(h) Parental environment effects",
                                              "MF_ID" = "(i) Parent's identity controlled for")),
             nrow = 3, ncol = 3, scales = "free_x", strip.position = "top", axes = "margins", axis.labels = "all_x") +
  meta_theme + theme(strip.background = element_blank(),
                     strip.text = element_text(size = 12),
                     panel.spacing.x = unit(0.1, "cm"),
                     panel.spacing.y = unit(0.15, "cm"),
                     plot.margin = margin(0.1, 0.1, 0.1, 0.1, "cm")) + xlab("Levels of the fixed effects")
faceted_moderators_comb_plot
#ggsave(faceted_moderators_comb_plot, filename = "faceted_moderators_comb_plot.png", bg = "white", width=30, height=30,  units = c("cm"))
ggsave(faceted_moderators_comb_plot, filename = "faceted_moderators_comb_plot.svg", bg = "white", width=30, height=30,  units = c("cm"))
```


### Human subset
```{r}
plotdf_human <- dd_human %>%
  mutate(ParSex = factor(recode(ParSex, "F"="Female","M"="Male"), levels = c("Female", "Male")),
         OffSex = factor(recode(OffSex, "F"="Female","M"="Male","Both"="Unspecified"), levels = c("Female", "Male","Unspecified")),
         SpermProdSeason = factor(SpermProdSeason, levels = c("Seasonal", "Continuous")),
         MethFact = factor(recode(MethFact, "qPCR"="qPCR","TRFSouthern"="TRF-SB","TRFInGel"="TRF-IG", "WGS"="WGS"), levels = c("qPCR","TRF-SB","TRF-IG","WGS")),
         OffAgeTL = factor(OffAgeTL, levels = c("Adult", "Juvenile","Both")),
         Tissue = factor(recode(Tissue,"Leucocytes"="Leucocytes","Erythrocytes"="Erythrocytes","Other"="Other"),
                         levels = c("Leucocytes", "Erythrocytes","Other")),
        # EnvCond = factor(EnvCond, levels = c("Wild", "Human")),
         W_B_PEff = factor(W_B_PEff, levels = c("Within", "Between", "Neither")),
         EnvEff = factor(recode(EnvEff,"Yes"="Accounted","No"="Not accounted"),levels = c("Accounted", "Not accounted")),
         MF_ID = factor(recode(MF_ID,"Yes"="Accounted","No"="Not accounted"), levels = c("Accounted", "Not accounted")))

# Unified moderators/fixed effects plot with facet_wrap
plotdf_long_human <- plotdf_human %>% pivot_longer(cols = c(MethFact, Tissue, SpermProdSeason, OffSex, OffAgeTL, ParSex, EnvEff, W_B_PEff, MF_ID), names_to = "Category", values_to = "Value") %>% mutate(Category = factor(Category, levels = c("ParSex","OffSex","SpermProdSeason","Tissue","OffAgeTL","MethFact","W_B_PEff","EnvEff","MF_ID"))) %>% mutate(Value = factor(Value))

faceted_moderators_comb_plot <- ggplot(plotdf_long_human, aes(x = Value)) +
  facet_wrap(~ Category,
             labeller = labeller(Category = c("ParSex" = "(a) Parental sex",
                                              "OffSex" = "(b) Offspring sex",
                                              "SpermProdSeason" = "(c) Sperm production seasonality",
                                              "Tissue" = "(d) Cell type",
                                              "OffAgeTL" = "(e) Offspring age at measurement",
                                              "MethFact" = "(f) Laboratory method",
                                              "W_B_PEff" = "(g) Within-/between-parent effects",
                                              "EnvEff" = "(h) Parental environment effects",
                                              "MF_ID" = "(i) Parent's identity controlled for")),
             nrow = 3, ncol = 3, scales = "free_x", strip.position = "top", axes = "margins", axis.labels = "all_x") +
  meta_theme + theme(strip.background = element_blank(),
                     strip.text = element_text(size = 12),
                     panel.spacing.x = unit(0.1, "cm"),
                     panel.spacing.y = unit(0.15, "cm"),
                     plot.margin = margin(0.1, 0.1, 0.1, 0.1, "cm")) + xlab("Levels of the fixed effects")
faceted_moderators_comb_plot
#ggsave(faceted_moderators_comb_plot, filename = "faceted_moderators_comb_plot.png", bg = "white", width=30, height=30,  units = c("cm"))
ggsave(faceted_moderators_comb_plot, filename = "faceted_moderators_comb_plot_human.svg", bg = "white", width=30, height=30,  units = c("cm"))
```

### Animal subset
```{r}
plotdf_animal <- dd_animal %>% mutate(ParSex = factor(recode(ParSex, "F"="Female","M"="Male"), levels = c("Female", "Male")),
         OffSex = factor(recode(OffSex, "F"="Female","M"="Male","Both"="Unspecified"), levels = c("Female", "Male","Unspecified")),
         SpermProdSeason = factor(SpermProdSeason, levels = c("Seasonal", "Continuous")),
         MethFact = factor(recode(MethFact, "qPCR"="qPCR","TRFSouthern"="TRF-SB","TRFInGel"="TRF-IG", "WGS"="WGS"), levels = c("qPCR","TRF-SB","TRF-IG","WGS")),
         OffAgeTL = factor(OffAgeTL, levels = c("Adult", "Juvenile","Both")),
         Tissue = factor(recode(Tissue,"Leucocytes"="Leucocytes","Erythrocytes"="Erythrocytes","Other"="Other"),
                         levels = c("Leucocytes", "Erythrocytes","Other")),
        # EnvCond = factor(EnvCond, levels = c("Wild", "Human")),
         W_B_PEff = factor(W_B_PEff, levels = c("Within", "Between", "Neither")),
         EnvEff = factor(recode(EnvEff,"Yes"="Accounted","No"="Not accounted"),levels = c("Accounted", "Not accounted")),
         MF_ID = factor(recode(MF_ID,"Yes"="Accounted","No"="Not accounted"), levels = c("Accounted", "Not accounted")))

# Unified moderators/fixed effects plot with facet_wrap
plotdf_long_animal <- plotdf_animal %>% pivot_longer(cols = c(MethFact, Tissue, SpermProdSeason, OffSex, OffAgeTL, ParSex, EnvEff, W_B_PEff, MF_ID), names_to = "Category", values_to = "Value") %>% mutate(Category = factor(Category, levels = c("ParSex", "OffSex", "SpermProdSeason", "Tissue", "OffAgeTL", "MethFact", "W_B_PEff", "EnvEff", "MF_ID"))) %>% mutate(Value = factor(Value))

# Manually add the missing row of OffSex Female count 0
missing_offsex_female <- tibble(
  Category = factor("OffSex", levels = levels(plotdf_long_animal$Category)),
  Value = factor("Female", levels = levels(plotdf_long_animal$Value)))

# Bind it only if it doesn’t already exist
plotdf_long_animal <- plotdf_long_animal %>%
  filter(!(Category == "OffSex" & Value == "Female")) %>%
  bind_rows(missing_offsex_female)

summary_counts <- plotdf_long_animal %>% count(Category, Value) %>% complete(Category = unique(plotdf_long_animal$Category),
                                                                             Value = unique(plotdf_long_animal$Value),
                                                                             fill = list(n = 0)) %>%
  rename(Count = n) %>%
  filter(Count > 0 | (Category == "OffSex" & Value == "Female")) %>%
  mutate(Count = ifelse(Category == "OffSex" & Value == "Female", 0, Count))

# faceted_moderators_comb_plot <- ggplot(plotdf_long_animal, aes(x = Value)) +
#   facet_wrap(~ Category,
#              labeller = labeller(Category = c("ParSex" = "(a) Parental sex",
#                                               "OffSex" = "(b) Offspring sex",
#                                               "SpermProdSeason" = "(c) Sperm production seasonality",
#                                               "Tissue" = "(d) Cell type",
#                                               "OffAgeTL" = "(e) Offspring age at measurement",
#                                               "MethFact" = "(f) Laboratory method",
#                                               "W_B_PEff" = "(g) Within-/between-parent effects",
#                                               "EnvEff" = "(h) Parental environment effects",
#                                               "MF_ID" = "(i) Parent's identity control")),
#              nrow = 3, ncol = 3, scales = "free_x", strip.position = "top", axes = "margins", axis.labels = "all_x") + meta_theme + theme(strip.background = element_blank(),
#                      strip.text = element_text(size = 12),
#                      panel.spacing.x = unit(0.1, "cm"),
#                      panel.spacing.y = unit(0.15, "cm"),
#                      plot.margin = margin(0.1, 0.1, 0.1, 0.1, "cm")) + xlab("Levels of the fixed effects")

meta_theme2 <- list(theme(panel.background = element_blank(),
                          panel.grid.major = element_blank(),
                          panel.grid.minor = element_blank(),
                          panel.border = element_rect(colour = "black", fill=NA, size=1),
                          axis.ticks = element_line(colour = "black"),
                          axis.text.x = element_text(size = 10, colour = "black", margin = margin(t = 5)),
                          axis.text.y = element_text(size = 10, colour = "black"),
                          axis.title.x = element_text(size = 12, colour = "black", margin = margin(t = 20)), 
                          axis.title.y = element_text(size = 12, colour = "black", margin = margin(r = 5))), 
                          #axis.line = element_line(colour = "black"),
                          geom_col(fill = "grey75", color = "black", width = 0.5),
                          geom_text(aes(label = Count), size = 3, vjust = -0.5),
                          scale_y_continuous(breaks = seq(0,140,20), limits = c(0,145), expand = c(0,0)),
                          ylab("Frequency"))
                   
faceted_moderators_comb_plot <- ggplot(summary_counts, aes(x = Value, y = Count)) + facet_wrap(~ Category,
             labeller = labeller(Category = c("ParSex" = "(a) Parental sex",
                                              "OffSex" = "(b) Offspring sex",
                                              "SpermProdSeason" = "(c) Sperm production seasonality",
                                              "Tissue" = "(d) Cell type",
                                              "OffAgeTL" = "(e) Offspring age at measurement",
                                              "MethFact" = "(f) Laboratory method",
                                              "W_B_PEff" = "(g) Within-/between-parent effects",
                                              "EnvEff" = "(h) Parental environment effects",
                                              "MF_ID" = "(i) Parent's identity controlled for")),
             nrow = 3, ncol = 3, scales = "free_x", strip.position = "top") + meta_theme2 + theme(strip.background = element_blank(),
                     strip.text = element_text(size = 12),
                     panel.spacing.x = unit(0.1, "cm"),
                     panel.spacing.y = unit(0.15, "cm"),
                     plot.margin = margin(0.1, 0.1, 0.1, 0.1, "cm")) + xlab("Levels of the fixed effects")
faceted_moderators_comb_plot

# ggsave(faceted_moderators_comb_plot, filename = "faceted_moderators_comb_plot.png", bg = "white", width=30, height=30,  units = c("cm"))
ggsave(faceted_moderators_comb_plot, filename = "faceted_moderators_comb_plot_animal.svg", bg = "white", width=30, height=30,  units = c("cm"))
```

## Combined plots with separate y-axis

```{r}
# parsex <- ggplot(plotdf, aes(ParSex)) + xlab("Parental sex") + meta_theme + labs(tag = "(c)") + theme(plot.margin = margin(0.05, 0.05, 1, 0.05, "cm"))
# offsex <- ggplot(plotdf, aes(OffSex)) + xlab("Offspring sex") + meta_theme + labs(tag = "(d)") + theme(plot.margin = margin(0.05, 0.25, 1, 0.05, "cm"))
# tissue <- ggplot(plotdf, aes(Tissue)) + xlab("Tissue") + meta_theme + labs(tag = "(e)") + theme(plot.margin = margin(0.05, 0.25, 1, 0.05, "cm"))
# offage <- ggplot(plotdf, aes(OffAgeTL)) + xlab("Offspring age\nat measurement") + meta_theme + labs(tag = "(f)") + theme(plot.margin = margin(0.05, 0.05, 1, 0.25, "cm"))
# method <- ggplot(plotdf, aes(MethFact)) + xlab("Laboratory method") + meta_theme + labs(tag = "(g)") + theme(plot.margin = margin(0.05, 0.05, 1, 0.05, "cm"))
# 
# season <- ggplot(plotdf, aes(SpermProdSeason)) + xlab("Sperm production\nseasonality") + meta_theme + labs(tag = "(h)") + theme(plot.margin = margin(0.05, 0.05, 0.05, 0.05, "cm"))
# wb <- ggplot(plotdf, aes(W_B_PEff)) + xlab("Within-/between-parent\neffects") + meta_theme + labs(tag = "(i)") + theme(plot.margin = margin(0.05, 0.05, 0.05, 0.05, "cm"))
# enveff <- ggplot(plotdf, aes(EnvEff)) + xlab("Environmental effects") + meta_theme + labs(tag = "(j)") + theme(plot.margin = margin(0.05, 0.05, 0.05, 0.05, "cm"))
# # envcond <- ggplot(plotdf, aes(EnvCond)) + xlab("Environmental conditions") + meta_theme + labs(tag = "(k)") + theme(plot.margin = margin(0.05, 0.05, 0.05, 0.05, "cm"))
# mfid <- ggplot(plotdf, aes(MF_ID)) + xlab("Parents' identity\ncontrol presence") + meta_theme + labs(tag = "(l)") + theme(plot.margin = margin(0.05, 0.05, 0.05, 0.05, "cm"))
# 
# # Combined plot
# moderators_comb_plot <- ggarrange(parsex, offsex, tissue, offage, method, season, wb, enveff, mfid,
#                                   align = "hv", ncol = 3, nrow = 3)
# #ggsave(moderators_comb_plot, filename = "moderators_comb_plot.png", bg = "white", width=15*3, height=15*1.25, units = c("cm"))
# ggsave(moderators_comb_plot, filename = "moderators_comb_plot.svg", bg = "white", width=30, height=30, units = c("cm"))

# ggsave(method, filename = "method.png", bg = "white", width=15, height=15, units = c("cm"))
# ggsave(tissue, filename = "tissue.png", bg = "white", width=15, height=15, units = c("cm"))
# ggsave(offsex, filename = "offsex.png", bg = "white", width=15, height=15, units = c("cm"))
# ggsave(offage, filename = "offage.png", bg = "white", width=15, height=15, units = c("cm"))
# ggsave(parsex, filename = "parsex.png", bg = "white", width=15, height=15, units = c("cm"))
# ggsave(wb, filename = "wb.png", bg = "white", width=15, height=15, units = c("cm"))
# ggsave(envcond, filename = "envcond.png", bg = "white", width=15, height=15, units = c("cm"))
# ggsave(enveff, filename = "enveff.png", bg = "white", width=15, height=15, units = c("cm"))
# ggsave(mfid, filename = "mfid.png", bg = "white", width=15, height=15, units = c("cm"))

```

## Studies per year, effect estimates per year, species frequency

```{r}
# Species per effect estimate
species_estimates <- ggplot(plotdf, aes(x=Species)) +
  geom_bar(stat = "count", width = 0.5, colour = "black", fill = "grey75") +
  geom_text(aes(label = after_stat(count)), stat = "count", size = 4, vjust = 0.5, hjust = -0.5) +
  scale_y_continuous(breaks = seq(0,100,20), limits = c(0,105), expand = c(0,0)) +
  xlab("Species per effect estimate") + ylab("Frequency") + labs(tag = "(a)") +
  coord_flip() +
  theme(plot.margin = margin(0.05, 0.05, 0.05, 0.05, "cm"),
        
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        
        axis.ticks = element_line(colour = "black"),
        axis.text.x = element_text(size = 12, colour = "black",margin = margin(t = 10)),
        axis.text.y = element_text(size = 10, colour = "black", margin = margin(r = 5)),
        axis.title.x = element_text(size = 12, colour = "black"), 
        axis.title.y = element_text(size = 12, colour = "black", margin = margin(r = 5)), 
        axis.line = element_line(colour = "black"))
#ggsave(species_estimates, filename = "species_estimates.png", bg = "white", width=20, height=20*0.5, units = c("cm"))
ggsave(species_estimates, filename = "species_estimates.svg", bg = "white", width=20, height=20*0.5, units = c("cm"))

# Effect estimates per year (from studies) PER EACH YEAR, also empty years
estimates_year <- ggplot(plotdf, aes(x=year)) +
  geom_bar(stat = "count", width = 0.5, colour = "black", fill = "grey75") +
  geom_text(aes(label = after_stat(count)), stat = "count", size = 4, vjust = -0.5) +
  scale_y_continuous(breaks = seq(0,35,5), limits = c(0,35), expand = c(0,0)) +
  xlab("Effect estimates per year") + ylab("Frequency") + labs(tag = "(b)") +
  theme(plot.margin = margin(0.05, 0.05, 0.05, 0.05, "cm"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.ticks = element_line(colour = "black"),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 10, colour = "black", margin = margin(t = 5)),
        axis.text.y = element_text(size = 12, colour = "black"),
        axis.title.x = element_text(size = 12, colour = "black", margin = margin(t = 15)), 
        axis.title.y = element_text(size = 12, colour = "black", margin = margin(r = 10)), 
        axis.line = element_line(colour = "black"))
#ggsave(estimates_year, filename = "estimates_year.png", bg = "white", width=16, height=16*0.75, units = c("cm"))
ggsave(estimates_year, filename = "estimates_year.svg", bg = "white", width=16, height=16*0.75, units = c("cm"))

# Combined plot
combined_study_species <- ggarrange(species_estimates, estimates_year,
                                     align = "hv", nrow = 1, ncol = 2, widths = c(1.25,1))
#ggsave(combined_study_species, filename = "combined_study_species.png", bg = "white", width=15*2.5, height=15*0.75, units = c("cm"))
ggsave(combined_study_species, filename = "combined_study_species.svg", bg = "white", width=15*2.5, height=15*0.75, units = c("cm"))
```

```{r}
###################
# Studies per year
d_year <- plotdf[!duplicated(plotdf$StudyID), ]
study_year <- ggplot(d_year, aes(year)) + xlab("Studies per year") + ylab("Frequency") + #labs(tag = "(X)") +
  geom_bar(stat = "count", width = 0.5, colour = "black", fill = "grey75") +
  geom_text(aes(label = after_stat(count)), stat = "count", size = 4, vjust = -0.5) +
  scale_y_continuous(breaks = seq(0,10,1), limits = c(0,8), expand = c(0,0)) +
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, "cm"),
        
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        
        axis.ticks = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12, colour = "black", margin = margin(t = 5)),
        axis.text.y = element_text(size = 12, colour = "black"),
        axis.title.x = element_text(size = 12, colour = "black", margin = margin(t = 15)), 
        axis.title.y = element_text(size = 12, colour = "black", margin = margin(r = 10)), 
        axis.line = element_line(colour = "black"))
#study_year

# Species per study
d_species <- plotdf[!duplicated(plotdf$StudyID), ] %>% group_by(Species)
species_study <- ggplot(d_species, aes(Species)) +
  geom_bar(stat = "count", width = 0.5, colour = "black", fill = "grey75") +
  geom_text(aes(label = after_stat(count)), stat = "count", size = 4, vjust = -0.5) +
  xlab("Species") + ylab("Count") +
  scale_y_continuous(breaks = seq(0, 30, 10), limits = c(0, 35), expand = c(0, 0)) +
  theme(plot.margin = margin(1, 0.05, 0.05, 3, "cm"),
        panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        
        axis.ticks = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 12, colour = "black", margin = margin(t = 5)),
        axis.text.y = element_text(size = 12, colour = "black"),
        axis.title.x = element_text(size = 12, colour = "black", margin = margin(t = 15)), 
        axis.title.y = element_text(size = 12, colour = "black", margin = margin(r = 10)), 
        axis.line = element_line(colour = "black"))
#species_study
```

```{r}
# Unused aterpillar plot
# dd$caterpillar <- if_else(d$Species %in% c("Homo sapiens"), "Human", "Other")
# m <- rma.mv(Zr,ZrVar,
#             mods = ~caterpillar,
#             random = list(~1|StudyID, ~1|Species, ~1|Phylogeny),
#             R = list(Phylogeny = PhyloMatrix),
#             method = "ML", data = dd, control = list(rel.tol = 1e-8)) # to avoid convergence problem
# 
# overall <- caterpillars(m,mod = "1", group = "Species",
#                         xlab = "Fisher’s z-transformed correlation coefficients",
#                         colerrorbar = "grey25", colpoint = "black", colpoly = "black",
#                         overall = T,k = T,g = F)
# overall + theme(
#   axis.line.y = element_blank(),
#   axis.line.x = element_line(colour = "black"),
#   plot.background = element_blank(),
#   panel.grid.major = element_blank(),
#   panel.grid.minor = element_blank(),
#   panel.border = element_blank())

# grouped <- caterpillars(m,
#                         mod = "caterpillar",
#                         group = "caterpillar",
#                         xlab = "Fisher’s z-transformed correlation coefficients",
#                         colerrorbar = "grey25", colpoint = "black", colpoly = "black",
#                         overall = T,k = T,g = F)
# grouped + theme(
#   axis.line.y = element_blank(),
#   axis.line.x = element_line(colour = "black"),
#   plot.background = element_blank(),
#   panel.grid.major = element_blank(),
#   panel.grid.minor = element_blank(),
#   panel.border = element_blank())
```


# Supplement: m1 without StudyID

```{r}
m1S <- rma.mv(Zr, ZrVar, random = list(~1|EstimateID, ~1|Species, ~1|Phylogeny),
                 R = list(Phylogeny = PhyloMatrix),
                 data = dd, method = "ML")
#summary(m1S)
confint_m1S <- confint(m1S)
confint_m1S
# Heterogeneity proportion
m1S.s2t <- sum(m1S$sigma2)+s2m
m1SI2total <- sum(m1S$sigma2)/m1S.s2t
m1SI2Estimate <- m1S$sigma2[1]/m1S.s2t
m1SI2Species <- m1S$sigma2[2]/m1S.s2t
m1SI2Phylogeny <- m1S$sigma2[3]/m1S.s2t
m1SI2Resid <- s2m/m1S.s2t
#LRT
S_est = rma.mv(Zr,ZrVar, random = list(~1|Species, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix),method = "ML", data = dd)
S_sp = rma.mv(Zr,ZrVar, random = list(~1|EstimateID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd)
S_ph = rma.mv(Zr,ZrVar, random = list(~1|EstimateID, ~1|Species), method = "ML", data = dd)

anova(m1S, S_est) # LRT for EstimateID - 408.9014 (<.0001)
anova(m1S, S_sp) # LRT for Species - 0.5043 (0.4776)
anova(m1S, S_ph) # LRT for Phylogeny - 0.7244 (0.3947)

m1S_human <- rma.mv(Zr, ZrVar, random = ~1|EstimateID,
                  data = dd[dd$SpeciesType == "Human",], method = "ML")
# summary(m1S_human)
confint_m1S_human <- confint(m1S_human)
confint_m1S_human
# Heterogeneity proportion
m1S_human.s2t <- sum(m1S_human$sigma2)+s2m # total variance
m1S_humanI2total <- sum(m1S_human$sigma2)/m1S_human.s2t
m1S_humanI2Estimate <- m1S_human$sigma2[1]/m1S_human.s2t
m1S_humanI2Resid <- s2m/m1S_human.s2t


m1S_animal <- rma.mv(Zr, ZrVar, random = list(~1|EstimateID, ~1|Species, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd[dd$SpeciesType == "Animal",],)
# summary(m1S_animal)
confint_m1S_animal <- confint(m1S_animal)
confint_m1S_animal
# Heterogeneity proportion
m1S_animal.s2t <- sum(m1S_animal$sigma2)+s2m # total variance
m1S_animalI2total <- sum(m1S_animal$sigma2)/m1S_animal.s2t
m1S_animalI2Estimate <- m1S_animal$sigma2[1]/m1S_animal.s2t
m1S_animalI2Species <- m1S_animal$sigma2[2]/m1S_animal.s2t
m1S_animalI2Phylogeny <- m1S_animal$sigma2[3]/m1S_animal.s2t
m1S_animalI2Resid <- s2m/m1S_animal.s2t

anS_est = rma.mv(Zr,ZrVar, random = list(~1|Species, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix),method = "ML", data = dd[dd$SpeciesType == "Animal",],)
anS_sp = rma.mv(Zr,ZrVar, random = list(~1|EstimateID, ~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd[dd$SpeciesType == "Animal",],)
anS_ph = rma.mv(Zr,ZrVar, random = list(~1|EstimateID, ~1|Species), method = "ML", data = dd[dd$SpeciesType == "Animal",],)

anova(m1S_animal, anS_est) # LRT for EstimateID - 15.7115 (<0.0001)
anova(m1S_animal, anS_sp) # LRT for Species - 1.1964 (0.2740)
anova(m1S_animal, anS_ph) # LRT for Phylogeny - 0.0000 (1.0000)

Smodels <- list(m1S, m1S_human, m1S_animal)
options(modelsummary_get = "broom")

m1S = modelsummary(
  Smodels, shape = term ~ model + statistic, fmt = fmt_sprintf("%.4f"),
  stars = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  estimate = "{estimate} ({std.error})",
  statistic = c("[{conf.low}, {conf.high}]", "{p.value} {stars}"),

  gof_map = c("nobs", "aic","bic","logLik","aicc", "deviance", "df.residual"))
m1S
#save_tt(m1S, output = "m1S_summary.docx",overwrite=T)

```

# Supplement: full output of model with two interactions (one insignificant) - minsig

```{r}
## Overall
# minsig <- rma.mv(Zr,ZrVar,
#              mods = ~ ParSex*OffSex + Tissue*OffAgeTL + OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix),
#              method = "ML", data = dd, control = list(rel.tol = 1e-8))
# summary(minsig)
# 
# confint_minsig <- confint(minsig)
# confint_minsig
# 
# # Heterogeneity proportion
# minsig.s2t <- sum(minsig$sigma2)+s2m # total variance
# minsigI2total <- sum(minsig$sigma2)/minsig.s2t
# minsigI2Study <- minsig$sigma2[1]/minsig.s2t
# minsigI2Estimate <- minsig$sigma2[2]/minsig.s2t
# minsigI2Species <- minsig$sigma2[3]/minsig.s2t
# minsigI2Phylogeny <- minsig$sigma2[4]/minsig.s2t
# minsigI2Resid <- s2m/minsig.s2t

### Subset into humans and animals

# Human
minsig_human <- rma.mv(Zr,ZrVar,
             mods = ~ParSex*OffSex + Tissue*OffAgeTL + OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID), method = "ML", data = dd[dd$SpeciesType == "Human",], control = list(rel.tol = 1e-8))
summary(minsig_human)
confint_minsig_human <- confint(minsig_human)
confint_minsig_human
# Heterogeneity proportion
minsig_human.s2t <- sum(minsig_human$sigma2)+s2m # total variance
minsig_humanI2total <- sum(minsig_human$sigma2)/minsig_human.s2t
minsig_humanI2Study <- minsig_human$sigma2[1]/minsig_human.s2t
minsig_humanI2Estimate <- minsig_human$sigma2[2]/minsig_human.s2t
minsig_humanI2Resid <- s2m/minsig_human.s2t


minsig_animal <- rma.mv(Zr,ZrVar,
             mods = ~ParSex*OffSex + Tissue*OffAgeTL + OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd[dd$SpeciesType == "Animal",], control = list(rel.tol = 1e-8))
minsig_animal
confint_minsig_animal <- confint(minsig_animal)
confint_minsig_animal
# Heterogeneity proportion
minsig_animal.s2t <- sum(minsig_animal$sigma2)+s2m # total variance
minsig_animalI2total <- sum(minsig_animal$sigma2)/minsig_animal.s2t
minsig_animalI2Study <- minsig_animal$sigma2[1]/minsig_animal.s2t
minsig_animalI2Estimate <- minsig_animal$sigma2[2]/minsig_animal.s2t
minsig_animalI2Phylogeny <- minsig_animal$sigma2[3]/minsig_animal.s2t
minsig_animalI2Resid <- s2m/minsig_animal.s2t 

### Save
models <- list()
#models[['Model 3']] <- minsig
models[['Model 3 - human subset']] <- minsig_human
models[['Model 3 - animal subset']] <- minsig_animal

options(modelsummary_get = "broom")

minsigsummary = modelsummary(
  models, shape = term ~ model + statistic, fmt = fmt_sprintf("%.4f"),
  stars = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  estimate = "{estimate} ({std.error})",
  statistic = c("[{conf.low}, {conf.high}]", "{p.value} {stars}"),

  gof_map = c("nobs", "aic","bic","logLik","aicc", "deviance", "df.residual"))
minsigsummary
save_tt(minsigsummary, output = "minsigsummary.docx",overwrite=T)
```

# Supplement: relevelled m2

```{r}
# releveled to male offspring ("M"), keep female parent ("F") dd$ParSex <- relevel(dd$ParSex, ref = "F")
dd$OffSex <- relevel(dd$OffSex, ref = "M")
# m2M <- rma.mv(Zr,ZrVar, mods = ~ParSex*OffSex + OffSex + ParSex+ SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID, ~1|Species,~1|Phylogeny), R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd, control = list(rel.tol = 1e-8), slab=paste(Author.s.))

m2M_human <- rma.mv(Zr,ZrVar, mods = ~ParSex*OffSex + OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID), method = "ML", data = dd[dd$SpeciesType == "Human",], control = list(rel.tol = 1e-8))

m2M_animal <- rma.mv(Zr,ZrVar, mods = ~ParSex*OffSex + OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID, ~1|Phylogeny), R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd[dd$SpeciesType == "Animal",], control = list(rel.tol = 1e-8))

models <- list(m2M_human, m2M_animal)
options(modelsummary_get = "broom")

m2Msummary = modelsummary(
  models, shape = term ~ model + statistic, fmt = fmt_sprintf("%.4f"),
  stars = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  estimate = "{estimate} ({std.error})",
  statistic = c("[{conf.low}, {conf.high}]", "{p.value} {stars}"),

  gof_map = c("nobs", "aic","bic","logLik","aicc", "deviance", "df.residual"))
m2Msummary
save_tt(m2Msummary, output = "m2Msummary.docx",overwrite=T)
```

```{r}
# releveled to unsegregated offspring ("Both"), keep female parent ("F") dd$ParSex <- relevel(dd$ParSex, ref = "F")
dd$OffSex <- relevel(dd$OffSex, ref = "Both")
# m2B <- rma.mv(Zr,ZrVar, mods = ~ParSex*OffSex + OffSex + ParSex+ SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID, ~1|Species,~1|Phylogeny), R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd, control = list(rel.tol = 1e-8), slab=paste(Author.s.))

m2B_human <- rma.mv(Zr,ZrVar, mods = ~ParSex*OffSex + OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID), method = "ML", data = dd[dd$SpeciesType == "Human",], control = list(rel.tol = 1e-8))

m2B_animal <- rma.mv(Zr,ZrVar, mods = ~ParSex*OffSex + OffSex + ParSex + SpermProdSeason + EnvEff + MF_ID + W_B_PEff + OffAgeTL + MethFact + Tissue, random = list(~1|StudyID, ~1|EstimateID, ~1|Species,~1|Phylogeny),R = list(Phylogeny = PhyloMatrix), method = "ML", data = dd[dd$SpeciesType == "Animal",], control = list(rel.tol = 1e-8))

models <- list(m2B_human, m2B_animal)
options(modelsummary_get = "broom")

m2Bsummary = modelsummary(
  models, shape = term ~ model + statistic, fmt = fmt_sprintf("%.4f"),
  stars = c("*" = 0.05, "**" = 0.01, "***" = 0.001),
  estimate = "{estimate} ({std.error})",
  statistic = c("[{conf.low}, {conf.high}]", "{p.value} {stars}"),

  gof_map = c("nobs", "aic","bic","logLik","aicc", "deviance", "df.residual"))
m2Bsummary
save_tt(m2Bsummary, output = "m2Bsummary.docx",overwrite=T)
```